### 2020-02-07 paper/sex_selection_spacing-ver3.tex
Sideways figure for spacing results

% \usepackage{endfloat}

@@

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_low_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_low_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_low_urban_all}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_low_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_low_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_low_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with no education}
\label{fig:bootstrap_low}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_med_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_med_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_med_urban_all}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_med_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_med_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_med_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with one to seven years of education}
\label{fig:bootstrap_med}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_urban_all}
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight to eleven years of education}
\label{fig:bootstrap_high}
\end{figure}

@@

\begin{figure}[htpb]
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_highest_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_highest_urban_all} 
    \end{minipage}
}
\\
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_highest_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_highest_rural_all} 
    \end{minipage}
} 
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with twelve or more years of education}
\label{fig:bootstrap_highest}
\end{figure}

>>>>

\usepackage{endfloat}

@@

% \begin{figure}[htpb]
% \centering
% \rotatebox[origin=c]{90}{\small{Urban}}
% \subfloat[Second Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell2_low_urban_all}
%     \end{minipage}
% } 
% \subfloat[Third Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell3_low_urban_all} 
%     \end{minipage}
% }
% \subfloat[Fourth Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell4_low_urban_all}
%     \end{minipage}
% }
% \\
% \rotatebox[origin=c]{90}{\small{Rural}}
% \subfloat[Second Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell2_low_rural_all}
%     \end{minipage}
% } 
% \subfloat[Third Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell3_low_rural_all} 
%     \end{minipage}
% } 
% \subfloat[Fourth Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell4_low_rural_all} 
%     \end{minipage}
% } 
% \caption{Estimated average spell length, sex ratio, and probability of 
% a next birth for women with no education}
% \label{fig:bootstrap_low}
% \end{figure}

\begin{sidewaysfigure}
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.31\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_low_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.31\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_low_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.31\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_low_urban_all}
    \end{minipage}
}
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with no education}
\label{fig:bootstrap_low}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\ContinuedFloat
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.31\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_low_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.31\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_low_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.31\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_low_rural_all} 
    \end{minipage}
} 
\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
a next birth for women with no education}
\label{fig:bootstrap_low}
\end{sidewaysfigure}

@@

% \begin{figure}[htpb]
% \centering
% \rotatebox[origin=c]{90}{\small{Urban}}
% \subfloat[Second Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell2_med_urban_all}
%     \end{minipage}
% } 
% \subfloat[Third Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell3_med_urban_all} 
%     \end{minipage}
% }
% \subfloat[Fourth Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell4_med_urban_all}
%     \end{minipage}
% }
% \\
% \rotatebox[origin=c]{90}{\small{Rural}}
% \subfloat[Second Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell2_med_rural_all}
%     \end{minipage}
% } 
% \subfloat[Third Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell3_med_rural_all} 
%     \end{minipage}
% } 
% \subfloat[Fourth Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell4_med_rural_all} 
%     \end{minipage}
% } 
% \caption{Estimated average spell length, sex ratio, and probability of 
% a next birth for women with one to seven years of education}
% \label{fig:bootstrap_med}
% \end{figure}

\begin{sidewaysfigure}
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_med_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_med_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_med_urban_all}
    \end{minipage}
}
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with one to seven years of education}
\label{fig:bootstrap_med}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\ContinuedFloat
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_med_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_med_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_med_rural_all} 
    \end{minipage}
} 
\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
a next birth for women with one to seven years of education}
\label{fig:bootstrap_med}
\end{sidewaysfigure}

@@

% \begin{figure}[htpb]
% \centering
% \rotatebox[origin=c]{90}{\small{Urban}}
% \subfloat[Second Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell2_high_urban_all}
%     \end{minipage}
% } 
% \subfloat[Third Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell3_high_urban_all} 
%     \end{minipage}
% }
% \subfloat[Fourth Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell4_high_urban_all}
%     \end{minipage}
% }
% \\
% \rotatebox[origin=c]{90}{\small{Rural}}
% \subfloat[Second Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell2_high_rural_all}
%     \end{minipage}
% } 
% \subfloat[Third Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell3_high_rural_all} 
%     \end{minipage}
% } 
% \subfloat[Fourth Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell4_high_rural_all} 
%     \end{minipage}
% } 
% \caption{Estimated average spell length, sex ratio, and probability of 
% a next birth for women with eight to eleven years of education}
% \label{fig:bootstrap_high}
% \end{figure}

\begin{sidewaysfigure}
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_urban_all} 
    \end{minipage}
}
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_urban_all}
    \end{minipage}
}
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight to eleven years of education}
\label{fig:bootstrap_high}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\ContinuedFloat
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_high_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_high_rural_all} 
    \end{minipage}
} 
\subfloat[Fourth Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell4_high_rural_all} 
    \end{minipage}
} 
\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
a next birth for women with eight to eleven years of education}
\label{fig:bootstrap_high}
\end{sidewaysfigure}

@@

% \begin{figure}[htpb]
% \centering
% \rotatebox[origin=c]{90}{\small{Urban}}
% \subfloat[Second Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell2_highest_urban_all}
%     \end{minipage}
% } 
% \subfloat[Third Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell3_highest_urban_all} 
%     \end{minipage}
% }
% \\
% \rotatebox[origin=c]{90}{\small{Rural}}
% \subfloat[Second Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell2_highest_rural_all}
%     \end{minipage}
% } 
% \subfloat[Third Spell]{
%     \begin{minipage}{0.29\textwidth}
%         \includegraphics[width=\textwidth]{bs_spell3_highest_rural_all} 
%     \end{minipage}
% } 
% \caption{Estimated average spell length, sex ratio, and probability of 
% a next birth for women with twelve or more years of education}
% \label{fig:bootstrap_highest}
% \end{figure}

\begin{sidewaysfigure}
\centering
\rotatebox[origin=c]{90}{\small{Urban}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_highest_urban_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_highest_urban_all} 
    \end{minipage}
}
\caption{Estimated average spell length, sex ratio, and probability of 
a next birth for women with twelve or more years of education}
\label{fig:bootstrap_highest}
\end{sidewaysfigure}

\begin{sidewaysfigure}
\ContinuedFloat
\rotatebox[origin=c]{90}{\small{Rural}}
\subfloat[Second Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell2_highest_rural_all}
    \end{minipage}
} 
\subfloat[Third Spell]{
    \begin{minipage}{0.29\textwidth}
        \includegraphics[width=\textwidth]{bs_spell3_highest_rural_all} 
    \end{minipage}
} 
\caption{(Continued) Estimated average spell length, sex ratio, and probability of 
a next birth for women with twelve or more years of education}
\label{fig:bootstrap_highest}
\end{sidewaysfigure}
